Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-08 paper.tex
introduce layout

\textcolor{red}{TODO: The rest of this text is organized as follows: in Section 2, ...}

@@

@@

@@

@@

>>>>

In this paper, we describe and motivate the design choices used in
building the library. First, in section \ref{sec:api}, we give the
central application programming interface (API). Then, in section
\ref{sec:implementation}, we describe the implementation trade-offs.
In section \ref{sec:weaknesses}, we analyze the limitations of the
technologies we rely on; and finally, in section \ref{sec:comparison}, we
position \emph{scikit-learn} with respect to other major projects.

@@

\label{sec:api}

@@

\label{sec:implementation}

@@

\label{sec:weaknesses}

@@

\label{sec:comparison}
